Integration of Multiple Constraints in ACG

### 2014-02-21 lenls/post-proc.tex
POST: Swap sigs in figs, embed biblio

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/double-acg.pdf}
    \caption{\label{fig:acg-comp-basic} Connecting form with meaning.}
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/serial-over-parallel.pdf}
    \caption{\label{fig:acg-comp-constr} Adding a constraint (Constraint).}
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/parallel-over-serial.pdf}
    \caption{\label{fig:acg-comp-sem} Distinguishing syntactic and
      semantic ambiguities (Elaboration).}
  \end{subfigure}
  \caption{\label{fig:acg-comp} Diagrams of systems of ACGs.}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=0.3\textheight]{../diagrams/final.pdf}
  \caption{\label{fig:gacg} A graphical ACG that implements two
      independent syntactic constraints and distinguishes syntactic and
      semantic ambiguities.}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=0.3\textheight]{../diagrams/diamond-grammar.pdf}
  \caption{\label{fig:diamond} The diamond-shaped G-ACG $\mathcal{D}$.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/story-single-cont.pdf}
    \caption{\label{fig:single-cont} An extraction constraint }
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/story-merged-conts.pdf}
    \caption{\label{fig:merged-conts} G-ACG merging the three extraction
      constraints.}
  \end{subfigure}
  \caption{\label{fig:conts} Combining the constraints on extraction.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/story-conts-elab.pdf}
    \caption{\label{fig:conts-elab} Elaborating the lexicon from syntax to
      strings. }
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{../diagrams/story-final-synth.pdf}
    \caption{\label{fig:final-synth} Adding our own syntactic constraints,
      $Neg$ and $Agr$.}
  \end{subfigure}
  \caption{\label{fig:final} Building the example grammar up to its final
    state.}
\end{figure}

@@

\bibliographystyle{splncs}
\bibliography{../biblio}

>>>>

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{diagrams/double-acg.pdf}
    \caption{\label{fig:acg-comp-basic} Connecting form with meaning.}
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{diagrams/serial-over-parallel.pdf}
    \caption{\label{fig:acg-comp-constr} Adding a constraint (Constraint).}
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{diagrams/parallel-over-serial.pdf}
    \caption{\label{fig:acg-comp-sem} Distinguishing syntactic and
      semantic ambiguities (Elaboration).}
  \end{subfigure}
  \caption{\label{fig:acg-comp} Diagrams of systems of ACGs.}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=0.3\textheight]{diagrams/final.pdf}
  \caption{\label{fig:gacg} A graphical ACG that implements two
      independent syntactic constraints and distinguishes syntactic and
      semantic ambiguities.}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=0.3\textheight]{diagrams/diamond-grammar.pdf}
  \caption{\label{fig:diamond} The diamond-shaped G-ACG $\mathcal{D}$.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{diagrams/story-single-cont.pdf}
    \caption{\label{fig:single-cont} An extraction constraint }
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{diagrams/story-merged-conts.pdf}
    \caption{\label{fig:merged-conts} G-ACG merging the three extraction
      constraints.}
  \end{subfigure}
  \caption{\label{fig:conts} Combining the constraints on extraction.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{diagrams/story-conts-elab.pdf}
    \caption{\label{fig:conts-elab} Elaborating the lexicon from syntax to
      strings. }
  \end{subfigure}
  \qquad
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[height=0.2\textheight]{diagrams/story-final-synth.pdf}
    \caption{\label{fig:final-synth} Adding our own syntactic constraints,
      $Neg$ and $Agr$.}
  \end{subfigure}
  \caption{\label{fig:final} Building the example grammar up to its final
    state.}
\end{figure}

@@

\begin{thebibliography}{10}

\bibitem{de2001towards}
De~Groote, P.:
\newblock Towards abstract categorial grammars.
\newblock In: Proceedings of the 39th Annual Meeting on Association for
  Computational Linguistics, Association for Computational Linguistics (2001)
  252--259

\bibitem{de2006towards}
De~Groote, P.:
\newblock Towards a montagovian account of dynamics.
\newblock In: Proceedings of SALT. Volume~16. (2006)

\bibitem{qian2011event}
Qian, S., Amblard, M.:
\newblock Event in compositional dynamic semantics.
\newblock In: Logical Aspects of Computational Linguistics.
\newblock (2011)

\bibitem{asher2011sdrt}
Asher, N., Pogodalla, S.:
\newblock Sdrt and continuation semantics.
\newblock In: New Frontiers in Artificial Intelligence. Volume 6797 of Lecture
  Notes in Computer Science.
\newblock (2011)

\bibitem{asher2011montagovian}
Asher, N., Pogodalla, S.:
\newblock A montagovian treatment of modal subordination.
\newblock In: Proceedings of SALT. Volume~20. (2011)  387--405

\bibitem{pogodalla2012controlling}
Pogodalla, S., Pompigne, F.:
\newblock Controlling extraction in abstract categorial grammars.
\newblock In: Formal Grammar. (2012)

\bibitem{degroote02}
de~Groote, P.:
\newblock Tree-adjoining grammars as abstract categorial grammars.
\newblock In: TAG+6, Proceedings of the sixth International Workshop on Tree
  Adjoining Grammars and Related Frameworks, Universit\`a di Venezia (2002)
  145--150

\bibitem{pogodalla2007generalizing}
Pogodalla, S.:
\newblock Generalizing a proof-theoretic account of scope ambiguity.
\newblock In: 7th International Workshop on Computational Semantics. (2007)

\bibitem{montague1973proper}
Montague, R.:
\newblock The proper treatment of quantification in ordinary english

\bibitem{perrier2007french}
Perrier, G.:
\newblock A french interaction grammar.
\newblock In: International Conference on Recent Advances in Natural Language
  Processing. (2007)

\bibitem{de2007type}
de~Groote, P., Maarek, S.:
\newblock Type-theoretic extensions of abstract categorial grammars.
\newblock ESSLLI 2007 (2007)

\end{thebibliography}
